### 2019-11-22 7_conclusion.tex
Edit conclusion.

\item Newer task-based systems have performance sufficient for
  weak scaling many HPC workloads, but more work is needed to strong
  scale the most demanding codes.

>>>>

\item Task Bench has proven effective in finding performance issues
  and has lead to substantial improvements in several of the systems
  we study.
